---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dplyr)
library(purrr)
```
# gregorian

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gregorian)](https://cran.r-project.org/package=gregorian)
[![Build Status](https://api.travis-ci.com/edgararuiz/gregorian.svg?branch=master)](https://travis-ci.com/edgararuiz/gregorian)
[![Coverage status](https://codecov.io/gh/edgararuiz/gregorian/branch/master/graph/badge.svg)](https://codecov.io/github/edgararuiz/gregorian?branch=master)
<!-- badges: end -->

Provides a robust date object. It also provides date calculation functions that work on top of the new object.  Many of the functions seamlessly convert `Date` and `character` objects into the new `gregorian_date` object. 

## Problem

```{r, eval = FALSE}
as.Date("-99-7-12")
```
```
Error in charToDate(x) : 
  character string is not in a standard unambiguous format
```

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/gregorian")
```
## Gregorian object

```{r}
library(gregorian)
as_gregorian("-99-7-12")
```


```{r}
born <- as_gregorian("-99-7-12")
```

```{r}
str(born)
```


```{r}
get_date()
```

## Date calculations

```{r}
diff_days(born, get_date())
```
```{r}
diff_dates(born, get_date())
```


```{r}
diff_calendar(born, get_date())
```

```{r}
add_days(get_date(), 365)
```

## Leap Year

```{r}
is_leap_year(2012)
```
```{r}
is_leap_year(2019)
```

## Day Rotation

```{r}
# Sunday plus one day (1 == Monday)
day_rotation(1, 7, 6) + 1
```

```{r}
# Sunday plus 100 days (2 == Tuesday)
day_rotation(100, 7, 6) + 1
```

## In the `tidyverse`

```{r}
library(dplyr)

dt <- tribble(~dates,
        as.Date("2014-12-12"),
        as.Date("1/1/1") - 1000,
        as.Date("1/1/1") - 365
        )

dt
```
```{r}
dt %>%
  extract_gregorian(dates, "full")
```

```{r}
dt %>%
  mutate(diff = diff_days(Sys.Date(), dates))
```


```{r}
library(purrr)

dt %>%
  mutate(new_date = map(dates, as_gregorian))
```
```{r}
dt %>%
  mutate(new_date = map_chr(dates, ~as_gregorian(.x)$full_date))
```

```{r}
dt %>%
  mutate(
    today_diff = map2_dbl(dates, Sys.Date(), diff_days)
    ) 
```
